Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Escape underscores in subsubsection titles
Explain subject_limit

\subsubsection{subject_limit}
\label{subs:subject_limit}

>>>>

\subsubsection{subject_limit}
\label{subs:subject_limit}
The subject line, i.e. the first line of a commit message, should be limited to 50 characters. This rule seems to have originated from a blog post by Tim Pope \cite{TP}, which is referenced by the Git manual \cite{OffGuide}. The reasoning behind it is, that the subject line is used by various tools and user interfaces to describe a commit in limited space.

Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does. Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without much language-specific effort.
